Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-22 awipev-CO2.Rmd
pH_seafet_mean and durafet SD added

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  )
d_all <- d_hour #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE))
#restore datetime, date which are mangled by the mutates above
d_all$datetime <- d_hour$datetime
d_all$date <- d_hour$date
d_all$month <- month(d_all$datetime)
```

@@

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- tibble(
  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
) %>% 
  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
                measure_date = dmy(measure_date, tz="UTC"),
                date = as.Date(datetime)) %>% 
  dplyr::rename(ph_s_sf = pH_s_seafet,
                ph_s_dur = pH_s_durafet,
                qflag_ph_s_sf = qflag_pH_s_seafet,
                qflag_ph_s_dur = qflag_pH_s_durafet)

@@

# Keep only flag = 2 for at/ct analysis 
# Keep only flag = 2 for pH durafet and seaFET.
d <- d%>%
  dplyr::mutate(ct = replace(ct, qflag_ct != 2, NA),
                at = replace(at, qflag_at != 2, NA),
                ph_s_sf = replace(ph_s_sf, qflag_ph_s_sf != 2, NA),
                ph_s_dur = replace(ph_s_dur, qflag_ph_s_dur != 2, NA))

# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
d$at <- d$at * 1.0002
d$ct <- d$ct * 1.0002

# mean at and ct
at_ct_mean <- d %>% 
#  group_by(datetime)%>%
  group_by(date) %>%
  dplyr::summarize(at_mean = mean(at, na.rm = TRUE),
                   ct_mean = mean(ct, na.rm = TRUE),
                   at_sd = sd(at, na.rm = TRUE), 
                   ct_sd = sd(ct, na.rm = TRUE)
                   )
d <- left_join(d, at_ct_mean, by='date') %>% 
  dplyr::select(datetime, date, temp_s_lab, ph_s_sf, ph_s_dur, location_flag, at, ct, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
  dplyr::distinct()

# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all %>%
                 dplyr::select(
                   c(
                     closest_datetime,
                     sal_fb,
                     temp_fb,
                     temp_mix,
                     sal_mix,
                     temp_insitu_11m,
                     temp_insitu_ctd,
                     pressure_insitu_ctd
                   )
                 ), by = "closest_datetime")

# Conversion of spec pH of in situ samples to in situ temp
pH_seafet <- d %>%
  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
pH_seafet <- pH_seafet %>% 
  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

# Conversion of spec pH of FerryBox samples to FerryBox temp
pH_durafet <- d %>%
  dplyr::filter(!is.na(ph_s_dur) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>% 
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, Pt = 0, Sit = 0))

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(date, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(date, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(date) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>%
  dplyr::group_by(date) %>%
  dplyr::summarize(
    sal_fb = mean(sal_fb, na.rm = TRUE),
    sal_mix = mean(sal_mix, na.rm = TRUE),
    temp_fb = mean(temp_fb, na.rm = TRUE),
    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
    at = mean(at, na.rm = TRUE),
    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
    ct = mean(ct, na.rm = TRUE),
    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
    temp_mix = mean(temp_mix, na.rm = TRUE),
    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
  )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='date')
discrete <- left_join(discrete, pH_durafet_mean, by='date')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ****** $SA$
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019

# pH calculated (at and ct) at Ferrybox sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
#discrete_no_na$pco2_calc<- carb$pCO2

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
#discrete_is_na$pco2_calc<- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)

# pH calculated (at and ct) at in situ (11 m) sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_mix)  & !is.na(temp_insitu_11m) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_mix)  | is.na(temp_insitu_11m) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_mix, T = discrete_no_na$temp_insitu_11m, P = 11/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$phcalc_insitu <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_insitu <- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_insitu <- NA
discrete_no_na$pco2_calc_insitu <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)

```{r Combine discrete and continous data, echo=FALSE}
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
                                          ph_s_sf_temp_insi, NA)) # only use ph spectro data when profiler was below 6 m

discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2_calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

@@

# pco2_contros_xts <-
#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
# pco2_contros_xts <-
#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
# dygraph(pco2_contros_xts,
#         group = "awipev",
#         main = "<i>p</i>CO<sub>2</sub>",
#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
#   dySeries(
#     axis = "y2",
#     "voltINT",
#     label = "voltINT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#   dySeries(axis="y2",
#     "voltEXT",
#     label = "voltEXT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "temp_insitu_ctd",
#     label = "temp_insitu_ctd",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "sal_fb",
#     label = "sal_fb",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "ph_s_sf_temp_insi",
#     label = "ph_s_sf_temp_insi",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
#     strokeWidth = 0,
#     pointSize = 4
#   ) %>%
#   dyHighlight(
#     highlightCircleSize = 8,
#     highlightSeriesBackgroundAlpha = 0.5,
#     hideOnMouseOut = TRUE
#   ) %>%
#   dyLegend(show = "follow")   %>%
#   dyAxis("y2",valueRange = c(-2,2))%>%
#   dyOptions(
#     drawGrid = TRUE,
#     drawPoints = TRUE,
#     pointSize = c(1, 8, 1),
#     useDataTimezone = TRUE
#   ) %>%
#   dyRangeSelector(height = 30, dateWindow = NULL)

>>>>

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
#d_all <
```

@@

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

@@

# Keep only flag = 2 for at/ct analysis 
# Keep only flag = 2 for pH durafet and seaFET.
d <- d%>%
  dplyr::mutate(ct= replace(ct, qflag_ct != 2, NA),
                at= replace(at, qflag_at != 2, NA),
                pH_s_seafet= replace(pH_s_seafet, qflag_pH_s_seafet != 2, NA),
                pH_s_durafet= replace(pH_s_durafet, qflag_pH_s_durafet != 2, NA))

# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
# AT
d$at <- d$at * 1.0002
#CT
d$ct <- d$ct * 1.0002

# Fill "at/ct" to all line with same day.
at_ct_mean <- d %>% 
  group_by(datetime)%>%
  dplyr::summarize(at_mean = mean(at, na.rm = T),
                   ct_mean = mean(ct, na.rm = T),
                   at_sd = sd(at, na.rm = T), 
                   ct_sd = sd(ct, na.rm = T)
                   )
d <- left_join(d, at_ct_mean, by='datetime')
# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

pH_durafet <- d %>%
#  dplyr::filter(!is.na(pH_s_durafet))
    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,ph_s_sf_temp_mix) %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = TRUE)  )
  #                 ph_s_sf_temp_mix_sd = round(sd(pH_seafet$ph_s_sf_temp_mix, na.rm = TRUE), digits = 4))

pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T) )
   #                ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = T)

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
                   temp_fb = mean(temp_fb, na.rm = T),
                   at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019

discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))

carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")

discrete_no_na$phcalc<- carb$pH
discrete_no_na$pco2_calc<- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc<- NA
discrete_is_na$pco2_calc<- NA
discrete <- rbind(discrete_no_na, discrete_is_na)
discrete <-discrete%>%dplyr::arrange(datetime)
```

```{r Combine discrete and continous data, echo=FALSE}

# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2_calc) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, ph_s_sf_temp_mix)%>%
#   dplyr::filter(!is.na(ph_s_sf_temp_mix))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

@@

# pco2_contros_xts <-
#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
# pco2_contros_xts <-
#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
# dygraph(pco2_contros_xts,
#         group = "awipev",
#         main = "<i>p</i>CO<sub>2</sub>",
#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
#   dySeries(
#     axis = "y2",
#     "voltINT",
#     label = "voltINT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#   dySeries(axis="y2",
#     "voltEXT",
#     label = "voltEXT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "temp_insitu_ctd",
#     label = "temp_insitu_ctd",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "sal_fb",
#     label = "sal_fb",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "ph_s_sf_temp_mix",
#     label = "ph_s_sf_temp_mix",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
#     strokeWidth = 0,
#     pointSize = 4
#   ) %>%
#   dyHighlight(
#     highlightCircleSize = 8,
#     highlightSeriesBackgroundAlpha = 0.5,
#     hideOnMouseOut = TRUE
#   ) %>%
#   dyLegend(show = "follow")   %>%
#   dyAxis("y2",valueRange = c(-2,2))%>%
#   dyOptions(
#     drawGrid = TRUE,
#     drawPoints = TRUE,
#     pointSize = c(1, 8, 1),
#     useDataTimezone = TRUE
#   ) %>%
#   dyRangeSelector(height = 30, dateWindow = NULL)

# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                        d_all$datetime <= as.POSIXct("2018-01-08") &
                        d_all$phINT < 8.04, NA, d_all$phINT)
d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                       d_all$datetime <= as.POSIXct("2018-01-08") &
                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
                        NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                        NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
                        NA, d_all$voltINT)
#periode 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
mean_voltEXT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
mean_TseaF_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  ) %>%
  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))
# Periode 2, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
mean_voltEXT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
